---
title: "Homework 1"
author: "Mengjiao Wu & Yaqi Dai"
date: "January 28, 2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Abstract




# 2. Introduction




# 3. Math Theory




# 4. Code chunks
Code chunk for calculating the true values and approximated values through Monte Carlo methods is shown as:
```{r, eval=FALSE}
Result_Matrix <- matrix(data = NA, nrow = 5, ncol = 9)
t_set <- c(0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72)
Result_Matrix[2,] <- as.matrix(pnorm(t_set))
N_set <- c(100, 1000, 10000)
Result_Matrix[1,] <- t_set
i = 3
for(N in N_set){
  j = 1
  for(t in t_set){
    x <- rnorm(N, mean = 0, sd = 1)
    Indicator_variable <- as.numeric(x <= t)
    Fi_t <- mean(Indicator_variable)
    Result_Matrix[i,j] <- Fi_t
    j = j+1
  }
  i = i+1
}
```
And code chunk for drawing box plots of bias at different t values is displayed as: 
```{r, eval=FALSE}
N_set <- c(100, 1000, 10000)
t_set <- c(0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72)

for (t in t_set){
  Bias <- matrix(data = NA, nrow = 3, ncol = 100)
  true_value <- pnorm(t)
  i = 1
  for(N in N_set){
    for(j in 1:100){
    x <- rnorm(N, mean = 0, sd = 1)
    Indicator_variable <- as.numeric(x <= t)
    Fi_t <- mean(Indicator_variable)
    Bias[i,j] <- Fi_t
    }
  i=i+1
  }

Bias_t <- t(Bias)
Bias_N <- cbind(N100 = Bias_t[,1],N1000 = Bias_t[,2],N10000 = Bias_t[,3])
boxplot(as.data.frame(Bias_N))
}
```

# 5. Table
Table containing true values and approximated values derived from Monte Carlo methods is shown as below: 
```{r echo=FALSE}
Result_Matrix <- matrix(data = NA, nrow = 5, ncol = 9)
t_set <- c(0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72)
Result_Matrix[2,] <- as.matrix(pnorm(t_set))
N_set <- c(100, 1000, 10000)
Result_Matrix[1,] <- t_set
i = 3
for(N in N_set){
  j = 1
  for(t in t_set){
    x <- rnorm(N, mean = 0, sd = 1)
    Indicator_variable <- as.numeric(x <= t)
    Fi_t <- mean(Indicator_variable)
    Result_Matrix[i,j] <- Fi_t
    j = j+1
  }
  i = i+1
}
Result_Table <- t(Result_Matrix) 
colnames(Result_Table) <- c("**t value**", "**True value**", 
                            "**N=100**", "**N=1000**", 
                            "**N=10000**")
knitr::kable(
  Result_Table, digits = 4, align = c(rep('c', 5)), 
  caption = "True & approximated values for different t values"
  )
```

# 6. Figures





# 7. Discussion and Conclusion

