---
title: "Homework 1"
author: "Mengjiao Wu & Yaqi Dai"
date: "January 28, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Abstract
This paper demonstrates the use of Monte Carlo methods in simulation of distribution function N(0,1) at different t values.

# 1. Introduction
Monte Carlo methods are mathematical techniques using repeated random samplings to obtain numerical results. It is mainly applied in three fields, which are optimization, numerical integration and generating plots from a probability distribution.

The purpose of this project is to calculate true values of distribution function N(0,1) at various t and simulate approximated values through Monte Carlo methods. By comparison of the true and simulated values, accuracy and efficiency of utilization of Monte Carlo methods can be examined.

The rest of this paper is organized as follows: In Section 2 and Section 3, basic math theory and the related chunks of R code are presented respectively. Results of one-time simulation and 100 repeated experiments in form of table and figures are identified in Section 4. Given in the final section of this report, brief discussion and conclusion are derived from the comparison of true values and simulated values.

# 2. Math Theory
Monte Carlo methods
equation
$$\Phi(t) = \int_{-\infty}^t{\frac{1}{\sqrt{2\pi}}}e^{-\frac{y^2}{2}}{\rm d}y$$

distribution function of N(0,1) equation
$$\Phi(t) = \int_{-\infty}^t{\frac{1}{\sqrt{2\pi}}}e^{-\frac{y^2}{2}}{\rm d}y$$

Monte Carlo methods equation
$$\Phi$$

# 3. Code chunks




# 4. Table
Table containing true values and approximated values derived from Monte Carlo methods is shown as below: 
```{r echo=FALSE}
Result_Matrix <- matrix(data = NA,nrow=5,ncol=9)
t_set <- c(0,0.67,0.84,1.28,1.65,2.32,2.58,3.09,3.72)
Result_Matrix[2,] <- as.matrix(pnorm(t_set))
N_set <- c(100,1000,10000)
Result_Matrix[1,] <- t_set
i=3
for(N in N_set){
  j=1
  for(t in t_set){
    x <- rnorm(N, mean=0, sd=1)
    Indicator_variable <- as.numeric(x <= t)
    Fi_t = mean(Indicator_variable)
    Result_Matrix[i,j] <- Fi_t
    j=j+1
  }
  i=i+1
}
Result_Table <- t(Result_Matrix) 
colnames(Result_Table) <- c("**t value**", "**True value**", 
                            "**N=100**", "**N=1000**", 
                            "**N=10000**")
knitr::kable(
  Result_Table, digits = 4, align = c(rep('c', 5)), 
  caption = "True & approximated values for different Ns"
  )
```

# 5. Figures




# 6. Discussion and Conclusion



